---
title: |
  2026 Industry Studies Association \
  Annual Conference
subtitle: |
  Program Schedule \
  June 3 - 5, 2026
format:
  pdf:
    toc: false
    number-sections: false
    highlight-style: haddock
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    mainfont: Avenir
    sansfont: Avenir
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      text: |
        \usepackage{xcolor}
        \definecolor{gis}{HTML}{E69F00}
        \definecolor{health}{HTML}{56B4E9}
        \definecolor{innovation}{HTML}{CC79A7}
        \definecolor{labor}{HTML}{B8860B}
        \definecolor{operations}{HTML}{0072B2}
        \definecolor{policy}{HTML}{D55E00}
        \definecolor{sustainability}{HTML}{009E73}
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
library(tidyverse)
library(knitr)
library(kableExtra)

# Read submissions data with type information
submissions <- read_csv(
  file.path('data', 'submissions.csv'),
  show_col_types = FALSE
) %>%
  mutate(id = as.character(id))

# Read self-organized panel details
self_sessions <- read_csv(
  file.path('data', 'self-sessions.csv'),
  show_col_types = FALSE
) %>%
  mutate(id = as.character(id))

# Read standalone panel sessions (these are interwoven into the schedule
# as panel discussion blocks, separate from paper sessions)
panels_raw <- read_csv(
  file.path('data', 'panels.csv'),
  show_col_types = FALSE
) %>%
  mutate(
    date_parsed = lubridate::mdy(date),
    day_name = case_when(
      date_parsed == as.Date("2026-06-03") ~ "Wednesday",
      date_parsed == as.Date("2026-06-04") ~ "Thursday",
      date_parsed == as.Date("2026-06-05") ~ "Friday",
      TRUE ~ format(date_parsed, "%A")
    ),
    start_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_start),
      format = "%Y-%m-%d %H:%M:%S"
    ),
    end_dt = as.POSIXct(
      paste(format(date_parsed, "%Y-%m-%d"), time_end),
      format = "%Y-%m-%d %H:%M:%S"
    ),
    room = str_trim(str_replace_all(room, "\\s+", " ")),
    track_color = case_when(
      category == "General Industry Studies" ~ "gis",
      category ==
        "Health Care Systems, Biotechnology, and Pharmaceuticals" ~ "health",
      category ==
        "Innovation, Entrepreneurship, and AI-Driven Transformation" ~ "innovation",
      category ==
        "Labor Markets, Organizations, and the Future of Work" ~ "labor",
      category ==
        "Operations, Supply Chain, and AI-Enhanced Industry 4.0" ~ "operations",
      category == "Public Policy and Global Competitiveness" ~ "policy",
      category ==
        "Sustainable Innovation, Energy, and Mobility" ~ "sustainability",
      TRUE ~ "black"
    )
  )

# Read full schedule (with time/room assignments)
schedule <- read_csv(
  file.path('data', 'schedule.csv'),
  show_col_types = FALSE
) %>%
  mutate(id = as.character(id))

# Merge submissions with schedule
sessions <- submissions %>%
  inner_join(schedule, by = "id") %>%
  mutate(
    is_self_organized = type == "self_organized_panel",
    panel_description = NA_character_
  )

# Add self-organized panel papers to sessions
# These papers share the same session_id as their parent panel submission
self_papers <- self_sessions %>%
  select(parent_id = id, authors, title, abstract) %>%
  left_join(
    sessions %>%
      filter(is_self_organized) %>%
      distinct(
        id,
        session_id,
        session_name,
        time_slot,
        room,
        date,
        day,
        start_time,
        end_time,
        time_order,
        category,
        type
      ),
    by = c("parent_id" = "id")
  ) %>%
  mutate(
    is_panel = FALSE,
    is_self_organized = FALSE
  )

# Replace self-organized panel entries with their constituent papers
sessions <- sessions %>%
  filter(!is_self_organized) %>%
  bind_rows(self_papers %>% select(-parent_id))

# is_panel is always FALSE (no panel_discussion type submissions)
sessions <- sessions %>%
  mutate(
    is_panel = if_else(is.na(is_panel), FALSE, is_panel)
  )

# Helper function to escape LaTeX special characters
escape_latex <- function(text) {
  if (is.na(text) || nchar(text) == 0) {
    return(text)
  }
  text <- str_replace_all(text, "\\\\", "\\\\textbackslash{}")
  text <- str_replace_all(text, "([&%$#_{}])", "\\\\\\1")
  text <- str_replace_all(text, "\\^", "\\\\textasciicircum{}")
  text <- str_replace_all(text, "~", "\\\\textasciitilde{}")
  return(text)
}

# Helper function for proper title case (keeps articles/conjunctions/prepositions lowercase)
proper_title_case <- function(text) {
  if (is.na(text) || nchar(text) == 0) {
    return(text)
  }

  # Words that should be lowercase (unless first or last word)
  lowercase_words <- c(
    "a",
    "an",
    "and",
    "as",
    "at",
    "but",
    "by",
    "for",
    "from",
    "in",
    "into",
    "of",
    "on",
    "or",
    "the",
    "to",
    "with",
    "vs",
    "via"
  )

  # Split into words
  words <- str_split(text, "\\s+")[[1]]

  # Title case each word
  result <- map_chr(seq_along(words), function(i) {
    word <- words[i]
    word_lower <- str_to_lower(word)

    # Always capitalize first and last word
    if (i == 1 || i == length(words)) {
      return(str_to_title(word))
    }

    # Keep lowercase words lowercase
    if (word_lower %in% lowercase_words) {
      return(word_lower)
    }

    # Otherwise title case
    return(str_to_title(word))
  })

  return(paste(result, collapse = " "))
}

# Short track codes and colors
sessions <- sessions %>%
  mutate(
    track_short = case_when(
      category == "General Industry Studies" ~ "GIS",
      category ==
        "Health Care Systems, Biotechnology, and Pharmaceuticals" ~ "Health",
      category ==
        "Innovation, Entrepreneurship, and AI-Driven Transformation" ~ "Innovation",
      category ==
        "Labor Markets, Organizations, and the Future of Work" ~ "Labor",
      category ==
        "Operations, Supply Chain, and AI-Enhanced Industry 4.0" ~ "Operations",
      category == "Public Policy and Global Competitiveness" ~ "Policy",
      category ==
        "Sustainable Innovation, Energy, and Mobility" ~ "Sustainability",
      TRUE ~ "Panel"
    ),
    track_color = case_when(
      category == "General Industry Studies" ~ "gis",
      category ==
        "Health Care Systems, Biotechnology, and Pharmaceuticals" ~ "health",
      category ==
        "Innovation, Entrepreneurship, and AI-Driven Transformation" ~ "innovation",
      category ==
        "Labor Markets, Organizations, and the Future of Work" ~ "labor",
      category ==
        "Operations, Supply Chain, and AI-Enhanced Industry 4.0" ~ "operations",
      category == "Public Policy and Global Competitiveness" ~ "policy",
      category ==
        "Sustainable Innovation, Energy, and Mobility" ~ "sustainability",
      TRUE ~ "black"
    ),
    title = map_chr(title, proper_title_case)
  )
```

```{r}
#| label: legend
#| results: asis
legend_data <- sessions %>%
  distinct(category, track_short, track_color) %>%
  filter(!is.na(category)) %>%
  arrange(category)

cat("```{=latex}\n")
cat("\\vspace{-2em}\n")
cat("\\textbf{\\large Track Categories}\\par\\smallskip\n")
cat("\\begin{itemize}\\setlength{\\itemsep}{2pt}\n")

for (i in seq_len(nrow(legend_data))) {
  r <- legend_data[i, ]
  cat(
    "  \\item \\textcolor{",
    r$track_color,
    "}{",
    escape_latex(r$category),
    "}\n",
    sep = ""
  )
}

cat("\\end{itemize}\n")
cat("\\vspace{0.5em}\\noindent\\hrulefill\\vspace{1em}\n")
cat("```\n\n")
```

```{r}
#| label: schedule
#| results: asis
# Build paper time blocks (one per time slot)
paper_blocks <- sessions %>%
  filter(!is.na(time_slot)) %>%
  group_by(time_slot) %>%
  summarize(
    day_name = first(day),
    start_dt = as.POSIXct(paste(first(as.character(date)), first(start_time))),
    end_dt = as.POSIXct(paste(first(as.character(date)), first(end_time))),
    .groups = "drop"
  ) %>%
  mutate(block_type = "paper", block_key = time_slot)

# Build panel time blocks (one per unique start time)
panel_blocks <- panels_raw %>%
  group_by(start_dt, end_dt, day_name) %>%
  summarize(.groups = "drop") %>%
  arrange(start_dt) %>%
  mutate(block_type = "panel", block_key = paste0("PANEL_", row_number()))

# Combine all blocks and sort chronologically
all_blocks <- bind_rows(
  paper_blocks %>% select(block_type, block_key, day_name, start_dt, end_dt),
  panel_blocks %>% select(block_type, block_key, day_name, start_dt, end_dt)
) %>%
  arrange(start_dt)

first_block <- TRUE

for (b in seq_len(nrow(all_blocks))) {
  block <- all_blocks[b, ]

  # Page break between blocks
  if (!first_block) {
    cat("\n\\newpage\n\n")
  }
  first_block <- FALSE

  # Session type label and time header — centered
  session_type <- if (b == 1) {
    "Plenary Session"
  } else if (block$block_type == "paper") {
    "Paper Sessions"
  } else {
    "Special Sessions"
  }

  time_label <- paste0(
    block$day_name,
    ", ",
    format(block$start_dt, "%I:%M %p"),
    " – ",
    format(block$end_dt, "%I:%M %p")
  )

  cat("\\begin{center}\n")
  cat("\\normalsize\\textit{", session_type, "}\\\\[0.3em]\n", sep = "")
  cat("\\Large\\textbf{", time_label, "}\n", sep = "")
  cat("\\end{center}\n\n")

  if (block$block_type == "paper") {
    ts <- block$block_key
    ts_sessions <- sessions %>%
      filter(time_slot == ts)

    # Get unique categories in this time slot, alphabetically
    track_order <- sort(unique(ts_sessions$category))

    # Loop through categories
    for (cat_name in track_order) {
      cat_sessions <- ts_sessions %>%
        filter(category == cat_name) %>%
        arrange(room)

      if (nrow(cat_sessions) == 0) {
        next
      }

      track_color <- unique(cat_sessions$track_color)[1]

      # Get unique sessions within this category
      unique_sess <- cat_sessions %>%
        distinct(session_id, session_name, room, is_panel) %>%
        arrange(room)

      for (k in seq_len(nrow(unique_sess))) {
        s <- unique_sess[k, ]

        # Repeat category header for each session
        cat("\n## \\textcolor{", track_color, "}{", cat_name, "}\n\n", sep = "")

        # Get session data
        session_data <- cat_sessions %>%
          filter(session_id == s$session_id)

        # Panel tag for panel discussion sessions only
        panel_tag <- if (s$is_panel) {
          " *(Panel Discussion)*"
        } else {
          ""
        }

        # Session title with room
        cat(
          "\n**",
          escape_latex(s$session_name),
          "**",
          panel_tag,
          " — Room ",
          s$room,
          "\n\n",
          sep = ""
        )

        if (s$is_panel) {
          # For panel sessions: show description and participants
          panel_info <- session_data %>%
            select(panel_description, authors) %>%
            slice(1)

          # Show panel description if available
          if (
            !is.na(panel_info$panel_description) &&
              nchar(panel_info$panel_description) > 0
          ) {
            cat(escape_latex(panel_info$panel_description), "\n\n")
          }

          # Show participants
          cat("**Participants:**\n\n")
          authors_list <- session_data %>%
            select(authors) %>%
            distinct()

          for (m in seq_len(nrow(authors_list))) {
            cat("- ", escape_latex(authors_list$authors[m]), "\n")
          }
          cat("\n")
        } else {
          # For regular sessions: show paper list
          papers <- session_data %>%
            arrange(id) %>%
            select(authors, title)

          for (m in seq_len(nrow(papers))) {
            cat(
              m,
              ". **",
              escape_latex(papers$authors[m]),
              "** — ",
              escape_latex(papers$title[m]),
              "\n\n",
              sep = ""
            )
          }
        }
      }
    }
  } else {
    # Panel block: render each panel in this time group
    group_panels <- panels_raw %>%
      filter(start_dt == block$start_dt) %>%
      arrange(category, room)

    for (k in seq_len(nrow(group_panels))) {
      p <- group_panels[k, ]

      cat(
        "\n## \\textcolor{",
        p$track_color,
        "}{",
        escape_latex(p$category),
        "}\n\n",
        sep = ""
      )

      cat(
        "\n**",
        escape_latex(p$title),
        "** *(Panel Discussion)*",
        " — Room ",
        escape_latex(p$room),
        "\n\n",
        sep = ""
      )

      # Moderator
      mod <- str_trim(p$moderator)
      if (!is.na(mod) && nchar(mod) > 0 && mod != "TBD") {
        cat("**Moderator:** ", escape_latex(mod), "\n\n", sep = "")
      }

      # Panelists
      pan_raw <- p$panelists
      if (
        !is.na(pan_raw) && str_trim(pan_raw) != "" && str_trim(pan_raw) != "TBD"
      ) {
        panelist_list <- str_split(pan_raw, "\n")[[1]] %>%
          str_trim() %>%
          .[nchar(.) > 0]
        cat("**Panelists:**\n\n")
        for (pan in panelist_list) {
          cat("- ", escape_latex(pan), "\n")
        }
        cat("\n")
      }

      # Description
      desc <- p$description
      if (!is.na(desc) && str_trim(desc) != "" && str_trim(desc) != "TBD") {
        cat(escape_latex(desc), "\n\n")
      }
    }
  }
}
```
